Secure Composition \\ of Robust and Optimising Compilers

### 2024-05-27 csf2/main.tex
flow nit

\MP{flow}
\MKin{
  % last sentence is before the example, which talks about compiler passes enforcing props
Whether or not compiler passes enforce certain security properties, it is important for a security-aware compiler to consider partial programs that interact with potentially malicious library code, since that code may lead to, e.g., memory--safety issues in the considered partial program.
}

>>>>

  % last sentence is before the example, which talks about compiler passes enforcing props
Whether or not compiler passes enforce certain security properties, it is important for a secure compiler to consider partial programs that interact with potentially malicious code, since the latter may lead to, e.g., memory-safety issues in the considered partial program.
